```{r init include=F}
cat('\014')
rm(list=ls())
library(crandb)
library(magrittr)
```

After running a local analysis to decide what packages you want, this routine will analyze packages and write binder scripts to achieve the desired image.

```{r packages}
p<-strsplit("abind,alluvial,assertthat,backports,base64enc,BH,bindr,bindrcpp,bit,bit64,bitops,blob,blockmodeling,bookdown,breakpoint,brew,broom,cairoDevice,caTools,changepoint,class,classInt,cli,clisymbols,cluster,coda,codetools,colorspace,crayon,curl,cvAUC,data.table,DBI,degreenet,dendextend,DEoptimR,devtools,DiagrammeR,DiagrammeRsvg,dichromat,digest,diptest,doParallel,doRNG,dotCall64,downloader,dplyr,e1071,EMD,ergm,ergm.count,evaluate,expm,extrafont,extrafontdb,fastmatch,fields,flexmix,forcats,foreach,forecast,foreign,fpc,fracdiff,gdata,geometry,ggdendro,ggformula,ggplot2,ggrepel,git2r,glmnet,glue,gplots,gridExtra,gtable,gtools,gWidgets,gWidgetsRGtk2,haven,hergm,highr,hms,htmltab,htmltools,htmlwidgets,httpuv,httr,igraph,influenceR,ipred,ISOcodes,iterators,jsonlite,kableExtra,kernlab,KernSmooth,knitr,labeling,latentnet,later,lattice,latticeExtra,lava,lazyeval,lda,LDAvis,lmtest,locfit,lpSolve,lsa,lubridate,magic,magrittr,mallet,maps,markdown,MASS,Matrix,matrixStats,maxent,mcgibbsit,mclust,memoise,microbenchmark,mime,miniCRAN,miniUI,mnormt,modeltools,mosaic,mosaicCore,mosaicData,msm,munsell,mvtnorm,network,networkDynamic,networksis,ngramr,nlme,NLP,nnet,nnls,numDeriv,openssl,phonTools,pillar,pkgconfig,pkgmaker,plogr,plyr,prabclus,praise,prediction,prettyunits,processx,prodlim,profvis,promises,proxy,psych,purrr,quadprog,qualtRics,quanteda,quantmod,R6,randomForest,RColorBrewer,Rcpp,RcppArmadillo,RcppEigen,RcppParallel,readr,registry,relevent,reshape2,reticulate,rgexf,RGoogleDrive,RGtk2,rJava,RJSONIO,rlang,rmarkdown,rngtools,robustbase,ROCR,RODBC,Rook,rpart,rprojroot,RQDA,RSpectra,RSQLite,rstudioapi,RTextTools,Rttf2pt1,rvest,scales,selectr,servr,shiny,sjlabelled,slam,sna,snakecase,SnowballC,sourcetools,spacyr,spam,SparseM,spData,SQUAREM,stargazer,statnet,statnet.common,stm,stmBrowser,stmCorrViz,stopwords,stringdist,stringi,stringr,SuperLearner,survival,tau,tergm,testthat,tibble,tidyr,tidyselect,timeDate,tinytex,tm,topicmodels,tree,trimcluster,trust,tseries,TSP,TTR,urca,uroot,utf8,V8,viridis,viridisLite,visNetwork,webshot,whisker,withr,wordcloud,xfun,xlsx,xlsxjars,XML,xml2,xtable,xts,yaml,zoo",",")[[1]]
```

Packages that have external dependencies are most difficult to install, as their dependencies must be installed manually before installing from R. The `SystemRequirements` field of a package `DESCRIPTION` field signals which packages required external dependencies.

```{r metadata}
m<-lapply(p,function(x) try(package(x),silent = T))
s<-sapply(m,function(x) try(x$SystemRequirements,silent = T))
names(s)<-p
noncran<-s[sapply(s,class)=='try-error']
s<-s[!(sapply(s,is.null)|sapply(s,class)=='try-error')]
```

Not everything listed here is gauranteed to fail, so manually checking is the only option.
```{r reset}
c<-0
```

```{r manual-log}
cat('\014')
c<-c+1
i<-names(s)[c]
cat('# ',i,'\n### ',s[[i]],'\n\n',sep='')
install.packages(i)
cat('\n',c,'/',length(s),'\n\n',sep='')
```

